### 2014-05-10 R/Neutral_simul.Rmd
Add funct to melt SAD to long & simul w/Replacement

```{r testKS_pomac467}
# Read simulation output and change from wide to long format NO TIME
#
meltDensityOut_NT <- function(fname,num_sp){
  den <- read.delim(fname)
  names(den)[1:5]<-c("GrowthRate","MortalityRate","DispersalDistance","ColonizationRate","ReplacementRate")

  # from 7 to 473 there are species densities
  # Put simpler names to variables to identify species
  names(den)[7:(6+num_sp)]<-as.character(1:num_sp)

  den1 <- melt(den,id.vars=c("MortalityRate","DispersalDistance","ColonizationRate","ReplacementRate"),measure.vars=c(7:473),variable.name="Species")

}

den <- read.delim("Exp467Density.txt")
names(den)[1:5]<-c("GrowthRate","MortalityRate","DispersalDistance","ColonizationRate","ReplacementRate")

# from 7 to 473 there are species densities
# Put simpler names to variables to identify species
names(den)[7:473]<-as.character(1:467)

den1 <- melt(den,id.vars=c("MortalityRate","DispersalDistance","ColonizationRate","ReplacementRate"),measure.vars=c(7:473),variable.name="Species")

@@

# Graph on pair with different mechanisms but not different SAD
#
# eks: 1 row data.frame with 2 sets of parms for which ks.test was done (fixed TIME)
# den1: full data in long format
#
mergePairSAD <- function(eks, den1){
# eks <- mks[61,]

  den2 <-merge(den1,eks,by.x=c(1:4),by.y=c(2:5))[,1:6]
  den2 <- den2[den2$value>0,]
  den2$parms <-paste(eks[,2:5],collapse="_")
  den2$Rank <- nrow(den2) - rank(den2$value) +1

  den3 <-merge(den1,eks,by.x=c(1:4),by.y=c(6:9))[,1:6]
  den3 <- den3[den3$value>0,]
  den3$parms <-paste(eks[,6:9],collapse="_")
  den3$Rank <- nrow(den3) - rank(den3$value) +1
  den2 <- rbind(den2,den3)

  }
# SE PODRIA HACER CON ddply para hacer varias filas del mks !!!!!

@@

debug(plotPairSAD)
psa <-mergePairSAD(mks[61,],den1)
# p.value = 
require(ggplot2)
g <- ggplot(psa,aes(x=Rank,y=log(value),colour=parms)) + geom_line()
g

@@

########### TEST THIS FUNCTION
den4 <- meltDensityOut_NT("Exp467Density.txt",nrow(ff))

@@

>>>>

```{r testKS_pomac467}

den1 <- meltDensityOut_NT("Simul/Exp467Density.txt",nrow(ff))

@@

# SE PODRIA HACER CON ddply para hacer varias filas del mks !!!!!

@@

psa <-mergePairSAD(mks[61,],den1)
# p.value = 
require(ggplot2)
g <- ggplot(psa,aes(x=Rank,y=log(value),colour=parms)) + geom_line()
g

@@

# Read all simulations and change to long format

den1 <- meltDensityOut_NT("Simul/Exp467Density.txt",nrow(ff))

pairKS_SAD(den1)

format(mks[mks$p.adjust>0.05,c(10:13,14:15)],digits=4)

nrow(mks[mks$p.adjust>0.05,c(10:13,14:15)])/nrow(mks)

psa <- mergePairSAD(mks[468,],den1)

require(ggplot2)

(g <- ggplot(psa,aes(x=Rank,y=log(value),colour=parms)) + geom_line())

@@

The proportion of equal distributions is 0.30 what happens if we test Dq
